Depression and suicidality as credible signals of need

### 2021-05-18 Paper.rmd
Fixed key. Added index.html

Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016]. These critics fail to acknowledge the central role of *conflict* in the signaling/bargaining models. Anger causes negative reactions in targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from others [@sell2009]. Aversive responses to bargaining are expected throughout the process, with potential helpers likely signaling the costliness of providing support in turn. Importantly, such responses do not prevent the delivery of meaningful benefits [@SymeHagen2021].

>>>>

Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016]. These critics fail to acknowledge the central role of *conflict* in the signaling/bargaining models. Anger causes negative reactions in targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from others [@SellEtAl2009]. Aversive responses to bargaining are expected throughout the process, with potential helpers likely signaling the costliness of providing support in turn. Importantly, such responses do not prevent the delivery of meaningful benefits [@SymeHagen2021].
